Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-04-30 vesicle_code/docs/permeableVes/Response2Refs.tex
yny

\begin{enumerate}
\item {\bf 
The referee wrote:
``It should be helpful for general readers to provide some exemplifying dimensional values of parameters (such as the radius of drop, viscosity of fluid, moduli of skeleton, shear or extension rate, and so on) in a few real world applications."}

\noindent
Response: We thank the referee for pointing out this oversight. We have provided estimates of dimensional values of parameters in the new \S II D, which is on page 11 in the revised manuscript.

\item {\bf 
The referee wrote:
``It is stated in the introduction that stretching (due to poration…)
give rise to enhanced membrane permeability to both water and
macromolecules such as ATP. Regarding ATP this is possible. In normal
conditions ATP is released thanks to protein change of conformation
that open channels and I am not sure the evoked permeability is a
similar phenomenon. A few words of clarification are needed."}

@@

@@

@@

@@

>>>>

\begin{enumerate}
\item {\bf 
The referee wrote:
``It is stated in the introduction that stretching (due to poration…)
give rise to enhanced membrane permeability to both water and
macromolecules such as ATP. Regarding ATP this is possible. In normal
conditions ATP is released thanks to protein change of conformation
that open channels and I am not sure the evoked permeability is a
similar phenomenon. A few words of clarification are needed."}

\noindent
Response: In recent experiments and simulations by Yaling Liu (Lehigh University), it is reported that under very large stress the spectrin network under a red blood cell membrane can be destroyed and the red blood cell membrane can rupture. As a result the hemoglobin inside the RBC is found to reduce in this process. We now see that the source of confusion arises from the fact that we associate such leakage to enhanced membrane permeability to macromolecules.

We agree with the referee that the ATP release is mostly understood when it is through the coupling between Px1 (activated by membrane tension) and CFTR (activated by membrane deformation), and it is not well understood yet how ATP can be released by diffusing through the membrane. We have thus modified this sentence to avoid confusion.

\noindent
Location:

@@

\noindent
Response: We thank the referee for this point. In our formulation, the permeation flux is proportional to the hydrostatic pressure and the normal component of the membrane force, which is the capillary pressure due to the Lagrange multiplier tension. The tangential force component due to tension field does not contribute to the permeation flux. To elucidate the relative contribution between the hydrostatic pressure and the normal component of the membrane force, we have added a short paragraph to illustrate how the relative contributions are in all cases.

\noindent
Location:

@@

\noindent
Response: We have mislabeled the $Ca_E$ in figure 5:  $Ca_E=1$ for the solid curves and the $Ca_E=10$ for the dashed curves. To address the effect of Capillary number on the relaxation of a semipermeable vesicle, we have continued the simulations for the cases of $Ca_E = 10$ much further to better illustrate the final reduced area at equilibrium.

@@

\noindent
Response: The shapes along the blue curve in Fig. 7B are equilibrium shapes that enclose a constant area but with an efflux (blue) and an influx (red) that adds to zero. Inset c illustrates the evolution from initial  the configuration (I) to the equilibrium (shape III), which corresponds to the case with the largest displacement on the blue curve. To better present all these results, we have taken out the insets (c) and (d) and moved them to the new Fig. 7 A and B. The new Fig. 7 C and D are the old Fig.  7 A and B.

\noindent
Location:

@@

\noindent
Response:  For the simulations in \S V for the two confinement cases, we have to use higher values of $\beta$ to keep the membrane tension below the threshold value (lysis tension) for membrane poration. {\bf In the manuscript I could not find the values of $\beta$ in \S V.} In addition, the far-field velocity is fixed in these simulations with confinement. We did not fix the pressure jump across the channel in these simulations. We have modified the text to provide a better explanation of this section.

\noindent
Location:
